Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_payment.tex
eidted payment section

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments.

@@

Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurs before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

@@

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)}}  \\
& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
\; = \; O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

It remains to show that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
We first use that $\sqrt{\cdot}$ is sublinear to bound
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
\]
(here we use the fact $\sqrt{n} \leq n$).
Next, we show that
$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
then, adding the two terms gives the desired bound.

By squaring the claimed statement and rearranging,
it is equivalent to show that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
Because $n \geq 2$,
a numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
and because $n \geq \frac{30 \sigma^3}{x^3}$,
we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.

\end{proof}

>>>>

As a first step towards bounding the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments.

@@

Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurred before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

@@

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)}}  \\
& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp\left(\frac{2}{p}\right)\right)
  + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
\; = \; O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

It remains to show that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
We first use that $\sqrt{\cdot}$ is sublinear to bound
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
\]
(here we use the fact $\sqrt{n} \leq n$).
Next, we show that
$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
then, adding the two terms gives the desired bound.

By squaring the claimed statement and rearranging,
it is equivalent to show that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
Because $n \geq 2$,
a numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
and because $n \geq \frac{30 \sigma^3}{x^3}$,
we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
\end{proof}
